\errorcontextlines 999999
\documentclass[userip,english,cpalette=Crimson]{lecture-fancy-paper}
\PassOptionsToPackage{threshold=1}{csquotes}
\PassOptionsToPackage{style=mmddyyyy,yearmonthsep={/},dayyearsep={/},monthdaysep={/}}{datetime2}
\usepackage[%
    sopra-listings={cpalette,numinpar},%
    sopra-tables={cpalette},%
    sopra-models,lecture,%
    lecture-bibliography={biber,style=numeric},%
    lithie-boxes={germanenv,autostyle},%
    lithie-task-boxes={cpalette},%
    lecture-links={patchurl}%
]{lithie-util}
\usepackage{ccicons}

\input{figures/color_definition.src}
\pagecolor{white!97!lightgray!99!paletteA}

\LoadBoxStyle{limerence}

\addbibresource{bibliography-collection/lithie.bib}

\makeatletter
\def\input@path{{source/}{figures/}}
\makeatother

\loadglsentries{glossary}
\usepackage{wrapfig,lipsum}
\usepackage[imgprefix={figures/asq_},command={Asq}]{lecture-personal}

\title{Limitations of Science}
\subtitle{The inexplicable, god, and its development in science}
\def\titleOfASQ{20\textsuperscript{th}~Century Thinking about Science}
\brief{\disablehyper\titleOfASQ~(\uc{asq})\\*\typesetAuthor, \lectureGetRegister{date}}
\addAuthor{Florian Sihler (florian.sihler@uni-ulm.de)}
\date\DTMtoday
\subject{ASQ, Elaboration}
\supervisor{Dr. Hans-Peter Eckle}
\authority{Ulm University, 2021}
\copyright{\href{https://creativecommons.org/licenses/by-nc-sa/2.0/}{CC BY-NC-SA 2.0}~~\ccLogo\ \ccAttribution\ \ccNonCommercialEU\ \ccShareAlike}

\newcommand*\footurl[3][]{\footnote{#1\url{#2}\quad(\DTMdate{#3})}}
\def\UrlBreaks{\do\/\do-}
\newcommand*\shortfooturl[4][]{\footnote{#1\href{#2}{#3}\quad(\DTMdate{#4})}}
\newcommand*\shortfootarchiveurl[4][]{\footnote{#1\href{#2}{#3}\quad(archived, \DTMdate{#4})}}
\newcommand*\footrefmark[1]{\textsuperscript{\disablehyper\hyperref[#1]{\thinspace\textcolor{gray}{see} \ref*{#1}}}}

% \;\smash{\raisebox{0.3\baselineskip}{\scalebox{0.35}{\faUniversity}}}

\usepackage{pbox}
\def\flocomment#1{\fcolorbox{paletteA}{shadeA}{\pbox{\linewidth}{\sffamily\textbf{\paletteA{Flo:}}~#1}}}

\def\formatshort#1#2{#1~\smash{\raisebox{.25\baselineskip}{\resizebox{!}{.25\baselineskip}{\pgfornament{14}}}}~#2}

\newcommand*\bce[1]{#1~BCE} % keep consistent with bibrefs
\SetBlockThreshold{0}

\usepackage{newunicodechar}
\newunicodechar{Ṭ}{\d{T}}
\newunicodechar{ṭ}{\d{t}}
\newunicodechar{ṣ}{\d{s}}
\newunicodechar{Ḥ}{\d{H}}
\newunicodechar{ī}{\=\i}
\newunicodechar{ā}{\=a}

\renewcommand*{\bibfont}{\normalfont\small}

\newcommand*\quoteshorten[1][$\mathellipsis$]{\textcolor{gray}{[}#1\textcolor{gray}{]}}

\begin{document}

\maketitle
% \lecturedivider

\begin{abstract}
    Since the dawn of mankind, humans are trying to understand how the world works.
    Their explanations, especially at the beginning, were dominated by a divine view of the world, which was supplemented by more and more science-based knowledge over time.

    This elaboration gives a brief overview of the history of the most important changes in the scientific worldview and their limitations, focusing on western cultures.
    Furthermore, the meaning of those limitations will be discussed, using the relationship to a god of some important scientific-contributors.

    It turns out that an (even imagined) limit in the perceivable worldview is not beneficial to scientific research. The union of religion and science even seems to be favorable.
    % and in no way can science ever fully replace religion
\end{abstract}

This work was created as an elaboration for the \uc{asq}: \say{\titleOfASQ} by \lectureGetRegister{supervisor} in the winter-semester 2020/2021 at the University of Ulm. The \LaTeXe-Documentclass was custom-made for this document by the author.

\input{1_introduction}
\input{2_history}
\input{3_theories}
\input{4_consciousness}
\input{5_discussion}
\input{6_conclusion}

\appendix
\defbibnote{generic@asq@prenote}{All links cited in the footnotes are not listed again. All created images (if not stated otherwise) have been created by the author (\typesetAuthor) using Ti\textit{k}Z.}
\printbibliography[prenote=generic@asq@prenote]

\end{document}